Political Polarization, Public Trust, and Healthcare Disparities: Unraveling COVID-19's Impact and Future Preparedness

### 2024-02-15 outputs/paper/paper.qmd
added estimand paragraph in intro , deleted files

>>>>

Our analysis seeks to estimate several key parameters, including the impact of political polarization on adherence to health guidelines, the association between social vulnerabilities (such as healthcare access, housing conditions, and ethnic demographics) and disparities in COVID-19 outcomes, and the influence of community health systems on disease trajectories. These estimands guide our methodology, data analysis, and interpretation of results, allowing us to comprehensively address the research questions.
